% =====================================================================
% SECTION II — RELATED WORK
% Uses ONLY the 25 verified references from IEEE_References_25.md
% =====================================================================

\section{Related Work}
\label{sec:related}

\textbf{Temporal forecasting.}
Lim et al.~\cite{lim2021tft} introduced Temporal Fusion
Transformers (TFT) with interpretable variable selection and
multi-horizon quantile heads---the architecture underpinning our
temporal branch. Hochreiter and Schmidhuber~\cite{hochreiter1997lstm}
established long short-term memory networks as the foundation for
sequential demand modeling. Makridakis et
al.~\cite{makridakis2022m5} benchmarked 61 forecasting methods
on 100{,}000 time series and confirmed WAPE and SMAPE as the
most robust metrics for zero-inflated demand. Hosseinnia and
Ghahnavieh~\cite{hosseinnia2023} survey deep learning in supply
chain management, confirming the persistent gap between research
accuracy and operational deployment.

\textbf{Graph neural networks for relational forecasting.}
Graph Attention Networks~\cite{velickovic2018gat} enable
attention-weighted structural aggregation over irregular topologies.
Kipf and Welling~\cite{kipf2017gcn} and Hamilton et
al.~\cite{hamilton2017graphsage} established the spectral and
inductive foundations of graph representation learning.
Jin et al.~\cite{jin2024survey} comprehensively survey GNNs
for time-series forecasting and classification; Jiang and
Luo~\cite{jiang2022gnn} synthesise spatio-temporal graph models
for traffic forecasting. Kosasih and
Brintrup~\cite{kosasih2022supply} show that GNNs recover latent
supply dependencies invisible to tabular models. Our GAT branch
extends this with typed attention across 4~(SupplyGraph) and
15~(USGS) heterogeneous edge relations.

\textbf{Hybrid temporal-graph models.}
Graph WaveNet~\cite{wu2019gwn} combines dilated causal convolution
with an adaptive graph convolution matrix, demonstrating that
learned graph structure outperforms fixed topology on traffic
forecasting. MST-GAT~\cite{ding2023mstgat} fuses spatial-temporal
signals via a multi-modal graph attention mechanism; Wu et
al.~\cite{wu2021gnn} provide a comprehensive taxonomy of GNN
architectures including temporal graph variants. Wasi et
al.~\cite{wasi2024gnn} benchmark GNNs on six supply-chain tasks,
showing a 10--30\% improvement over classical baselines. None of
these models learn a \emph{per-instance}, context-conditioned
modality weight between temporal and structural branches.

\textbf{Uncertainty and interpretability.}
Wen et al.~\cite{wen2017quantile} introduced multi-horizon
quantile recurrent forecasters; Gneiting and
Raftery~\cite{gneiting2007scoring} establish the theoretical
foundation for calibrated interval scoring. Lundberg and
Lee~\cite{lundberg2017shap} argue for post-hoc attribution; our
$\alpha$ trajectory provides built-in training-time
interpretability without additional explanation passes. The
IEA~\cite{iea2024minerals} documents critical mineral demand
surges that motivate forecast-driven procurement planning.
