% =====================================================================
% SECTION VIII — CONCLUSION
% File: section8_conclusion.tex
% =====================================================================

% ------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
% ------------------------------------------------------------------

We presented ATSF, an Adaptive Temporal-Structural Fusion model
that learns a per-instance scalar weight $\alpha$ to balance
temporal transformer and graph attention representations for
multi-horizon demand forecasting. The model demonstrates that the
optimal modality balance is dataset-specific and can be recovered
end-to-end without manual tuning. On daily FMCG data, the model
correctly identifies temporal dominance ($\alpha{=}0.919$) and
reduces WAPE by $30.1\%$ relative to the best neural alternative.
On annual mineral commodity data, it identifies a mixed regime
($\alpha{=}0.489$) and achieves a 95\% confidence interval for
WAPE entirely below the strongest classical baseline. Perfect
Wilcoxon consistency across five seeds ($\text{stat}{=}0$,
$p{=}0.0625$) confirms reproducibility.

Future work will explore extending multi-relational graph
construction to include dynamic edge weights, applying the
adaptive fusion mechanism to longer USGS time series as more
annual data become available, and evaluating the risk scoring
layer against real procurement outcomes in a prospective study.

\smallskip
\noindent\textbf{Disclosure.} This research did not receive any
specific grant from funding agencies in the public, commercial,
or not-for-profit sectors. No conflicts of interest are declared.
All code and model weights will be released upon acceptance.
